### 2020-10-02 report/draft.tex
tidied, updated and fixed report

    We chose gametogenesis-induced extra mortality ($d$), growth rates ratio ($r_p:r_{f1}$), day of appearance ($t_{F_{1}I}$), and duration of the growth block (as the block's end day $t_{GE}$) as salient parameters to explore within the simulation to better understand how event timing impacts over F1 survival rate (\textbf{Figs.~\ref{gon1},~\ref{gon2},~\ref{gon3},~\ref{gon4}}).
    The range of variations of the different parameters, as well as the value of the other biological parameters, are reported in \textbf{Table~\ref{tbl1}}.
    We deployed an interactive version of the model at the URL \url{https://arfalas.shinyapps.io/pns_toy/}, code and figures are available on \url{https://github.com/bhym/Stec} ({\color{red} currently private})

@@

    Finally, $\delta$ is an extra mortality term defined as
    \[
      \begin{cases}
        d & \mbox{if } t < t_{BE} \\
        0 & \mbox{if } t > t_{BE}
      \end{cases}
    \]
    \subsection*{Parameters}
      \begin{table}[h]
         \begin{tabular}{@{}llccr@{}}
          \toprule
            \textbf{Variable}&\textbf{Meaning} & \textbf{Value} & \textbf{Units} & \textbf{Reference}\\
          \midrule
            ${[P]}_{0}$     & initial concentration of P cells           & cells/ml          & 4E3           & The experiment detailed in the paper\\
            $\alpha$        & relative amount of F1 cells                & ---               & 0.012         & The experiment detailed in the paper\\
            $k$             & nitrogen multiplication factor             & ---               & 1.2           & ---\\
            $g_{0, P}$      & basal growth rate for parental generation  & $\text{day}^{-1}$ & {[0.1,5]}     & Explored via simulations\\
            $g_{0, F_{1}}$  & basal growth rate for offspring generation & $\text{day}^{-1}$ & 1             & ---\\
            $t_{BE}$        & end day of the growth arrest               & day               & ${[1,9]}$     & Explored via simulations\\
            $t_{F_{1}I}$    & day of appearence of the offspring         & day               & ${[1,9]}$     & Explored via simulations\\
            $d$             & gametogenesis-induced extra mortality      & day               & ${[0.1,0.9]}$ & Explored via simulations\\
            $L_{0,P}$       & starting length for P cells                &$\mu$m             & 40            & The experiment detailed in the paper\\
            $L_{0,{F_{1}}}$ & starting length for P cells                &$\mu$m             & 55            & The experiment detailed in the paper\\
            $j$             & length lower limit for cell division       &$\mu$m             & 38            & D'Alelio et al. (2009)\\
          \bottomrule
        \end{tabular}
        \caption{Values and ranges for model parameters}\label{tbl1}
      \end{table}
%
\pagebreak
%
  \section*{Results}
    \begin{figure}[h]
      \centering
      \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\linewidth]{imgs/a.pdf}
      \end{subfigure}
      %
      \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\linewidth]{imgs/b.pdf}
      \end{subfigure}

      \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\linewidth]{imgs/c.pdf}
      \end{subfigure}
      %
      \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\linewidth]{imgs/d.pdf}
      \end{subfigure}
      \caption{\textbf{2D plot of ranges of biomass ratio between P and F1} after 10 days of simulation for paired values of parameters (axes labels). Subplots represent growth arrests of different length.}\label{gon4}
    \end{figure}
%
\pagebreak
%
    \subsection*{Tabular data}
        \begin{table}[h]
          \begin{subtable}[h]{0.45\textwidth}
            \centering
            \input{tbls/ranr0p-ranalp_1.tex}
            \caption{Duration of the growth block: 1 day}
          \end{subtable}
          %
          \begin{subtable}[h]{0.45\textwidth}
            \centering
            \input{tbls/ranr0p-ranalp_2.tex}
            \caption{Duration of the growth block: 2 days}
          \end{subtable}

          \vspace{1cm}
          \begin{subtable}[h]{0.45\textwidth}
            \centering
            \input{tbls/ranr0p-ranalp_3.tex}
            \caption{Duration of the growth block: 3 days}
          \end{subtable}
          %
          \begin{subtable}[h]{0.45\textwidth}
            \centering
            \input{tbls/ranr0p-ranalp_4.tex}
            \caption{Duration of the growth block: 4 days}
          \end{subtable}

          \vspace{1cm}
          \begin{subtable}[h]{0.45\textwidth}
            \centering
            \input{tbls/ranr0p-ranalp_5.tex}
            \caption{Duration of the growth block: 5 days}
          \end{subtable}
          %
          \begin{subtable}[h]{0.45\textwidth}
            \centering
            \input{tbls/ranr0p-ranalp_6.tex}
            \caption{Duration of the growth block: 6 days}
          \end{subtable}
           \caption{Tabular data for $(\alpha, r_p:r_{f1})$ parameter subspace}\label{tbl2}
        \end{table}
   %
  \section*{Assumptions} 
    \begin{enumerate}
      \item I assume that net growth rate is the balance between size-dependent cell proliferation and death
      \item I assume that P suffers extra mortality during growth arrest due to gametogenesis
      \item I assume that lenght decreses 1 um after each division
      \item I assume that P has reached the environmental carrying capacity before starting the simulation
    \end{enumerate}
\end{document}

>>>>

    We chose gametogenesis-induced extra mortality ($d$), growth rates ratio ($r_p:r_{f1}$), day of appearance ($t_{F_{1}I}$), and duration of the growth arrest (as the arrest's end day $t_{GE}$) as salient parameters to explore within the simulation to better understand how event timing impacts over F1 survival rate (\textbf{Fig.~\ref{swep}}).
    The range of variations of the different parameters, as well as the value of the other biological parameters, are reported in \textbf{Table~\ref{tbl1}}.
    We deployed an interactive version of the model at the URL \url{https://arfalas.shinyapps.io/pns_toy/}, code and figures are available on \url{https://github.com/bhym/Stec} ({\color{red} currently private})

@@

    Finally, $\delta$ is an extra mortality term defined as
    \[
      \begin{cases}
        d & \mbox{if } t < t_{BE} \\
        0 & \mbox{if } t > t_{BE}
      \end{cases}
    \]
    \subsection*{Parameters}
      \begin{table}[h]
         \begin{tabular}{@{}llccr@{}}
          \toprule
            \textbf{Variable}&\textbf{Meaning} & \textbf{Value} & \textbf{Units} & \textbf{Reference}\\
          \midrule
            ${[P]}_{0}$     & initial concentration of P cells           & cells/ml          & 4E3           & The experiment detailed in the paper\\
            $\alpha$        & relative amount of F1 cells                & ---               & 0.012         & The experiment detailed in the paper\\
            $k$             & nitrogen multiplication factor             & ---               & 1.2           & ---\\
            $g_{0, P}$      & basal growth rate for parental generation  & $\text{day}^{-1}$ & {[0.1,5]}     & Explored via simulations\\
            $g_{0, F_{1}}$  & basal growth rate for offspring generation & $\text{day}^{-1}$ & 1             & ---\\
            $t_{BE}$        & end day of the growth arrest               & day               & ${[1,9]}$     & Explored via simulations\\
            $t_{F_{1}I}$    & day of appearence of the offspring         & day               & ${[1,9]}$     & Explored via simulations\\
            $d$             & gametogenesis-induced extra mortality      & day               & ${[0.1,0.9]}$ & Explored via simulations\\
            $L_{0,P}$       & starting length for P cells                &$\mu$m             & 40            & The experiment detailed in the paper\\
            $L_{0,{F_{1}}}$ & starting length for P cells                &$\mu$m             & 55            & The experiment detailed in the paper\\
            $j$             & length lower limit for cell division       &$\mu$m             & 38            & D'Alelio et al. (2009)\\
          \bottomrule
        \end{tabular}
        \caption{Values and ranges for model parameters}\label{tbl1}
      \end{table}
%
\pagebreak
%
  \section*{Results}
    \begin{figure}[h]
      \centering
      \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\linewidth]{imgs/a.pdf}
      \end{subfigure}
      %
      \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\linewidth]{imgs/b.pdf}
      \end{subfigure}
      \caption{\textbf{2D plot of ranges of biomass ratio between P and F1} after 10 days of simulation for paired values of parameters (axes labels). Subplots represent growth arrests of different length.}\label{swep}
    \end{figure}
  %
    \begin{table}[h]
      \centering
      {%
      \begin{subtable}{.5\textwidth}\centering\scriptsize
        {\input{tbls/randfac-ranr0p_5.tex}}
        \caption{$d, r_p:r_{f1}$}
      \end{subtable}

      \vspace{0.5cm}
      \begin{subtable}{.5\textwidth}\centering\scriptsize
        {\input{tbls/ranalp-ranr0p_5.tex}}
        \caption{$\alpha, r_p:r_{f1}$}
      \end{subtable}
       \caption{Tabular data for different parameter 2D subspaces and growth arrest duration of 5 days}\label{tbl2}
     }
    \end{table}
%
  \section*{Assumptions} 
    \begin{enumerate}
      \item I assume that net growth rate is the balance between size-dependent cell proliferation and death
      \item I assume that P suffers extra mortality during growth arrest due to gametogenesis
      \item I assume that lenght decreses 1 um after each division
      \item I assume that P has reached the environmental carrying capacity before starting the simulation
    \end{enumerate}
\end{document}
